\documentclass[fontsize=11pt]{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}

\title{CSC111 Project 2 Proposal: TODO FILL IN YOUR PROJECT TITLE HERE}
\author{Xin Lei Lin, Evan Su, Rick Chen, Yi He (Robert) Li}
\date{\today}

\begin{document}
\maketitle

\section*{Problem Description and Research Question}
JetSetGo


Tasks
1. Graph algorithms (shortest path djikstras, depth first search for existence, 
each vertex is a GPS coordinate -- kosajaru's algorithm) 

% 2. Machine learning to recommend where people should go :)
 NO! Train it hahaha. ===> if we have time..

or. hard. code.
to recommend/scoring system

3. Scipy to graph the map

4. Database/flask backend with mysql python.?
% https://www.w3schools.com/python/python_mysql_create_db.asp

is it necessary?
-- > we need to identify who the user is.
(optional)

Just create a bunch of json files with the right names

5. Clustering algorihtms? KNN, SVM, (scikit-learn) ==> we would have to have user, and to recommend places.

cosine similarity with the user , to recommend the user where to go

6. 


--------------
steps:
1. After we know who the user is

2. user comes in, and says his location; "Hi I am currently in Dubai"

3. Clustering would be for like, recommending where to.
    3a) 1 model that says Hello, these places are very different!
    ab) 1 model that says, hello, these places are very similar.

4. Then, the user chooses the place where they want to go. Or types their own place
    4a) Give the shortest path (weighted graph), also with the price.
        4aa) Notice that we are using directed graphs.
    
    4b) Say time its' gonna take, and mashallah go fly.

    4c) Recommend shortest, cheapest and "best value" ==> we define it

5. Evan for frontend TTT WAAW SAINT MASHALLAH THANK YOU.
    




\section*{Computational Plan}

TODO

\section*{References}

TODO

% NOTE: LaTeX does have a built-in way of generating references automatically,
% but it's a bit tricky to use so you are allowed to write your references manually
% using a standard academic format like MLA or IEEE.
% See project proposal handout for details.

\end{document}